---
title: "gov1005_final"
author: "Melissa Gayton"
date: "10/18/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(tidyverse)
library(knitr)
library(readxl)
```

```{r, message = FALSE}
included_only <- read_csv("SelectCovariates_13 Oct 2016.csv")

all_data <- read_csv("philly_vars.csv")

labels <- read_excel("Covariate_labels.xlsx")
```

The data I plan to use is from a study conducted by the Access to Justice Lab at Harvard Law School, where I work. The lab conducted a randomized control trial to evaluate the accessibility of divorce in Philadelphia, and basically found it was much more expensive to get a divorce than it really should be. For my final project, I'll be visualizing data from the study. For the purposes of this project, the data has been de-identified to maintain participants' privacy. Among those included in the study, there are 311 observations and 57 variables. The data is in the file called "SelectCovariates_13 Oct 2016.csv". Among all those who went through intake, including those excluded due to either them or their spouse having already file dfor divorce, there are 378 observations of 442 variables, which can be found in the file "philly_vars.csv." A guide to the variables can be found in "Covariate_labels.xlsx".
